---
title: "p8105_hw2_dk2759"
author: "Darwin Keung"
date: "10/4/2018"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing and Cleaning Data

```{r import data}
library(tidyverse)

options(tibble.print_min = 5)

## Reading the data NYC Subway Entrance and Exit Data
NYC_Subway_Data = read_csv(file = "./Data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv")
names(NYC_Subway_Data)
NYC_Subway_Data = janitor::clean_names(NYC_Subway_Data)
names(NYC_Subway_Data)

## Looking at data for errors
NYC_Subway_Data
skimr::skim(NYC_Subway_Data)
select(NYC_Subway_Data, line, station_name, station_latitude, station_longitude, route1,   litter_number, gd0_weight, pups_born_alive)

as.numeric()
```

Clean the data; retain line, station, name, station latitude / longitude, routes served, entry, vending, entrance type, and ADA compliance. Convert the entry variable from character (YES vs NO) to a logical variable



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
