---
title: "p8105_hw2_dk2759"
author: "Darwin Keung"
date: "10/4/2018"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library("dplyr")
```

## Problem 1: NYC Subway Data 

Importing Data

```{r import data}
options(tibble.print_min = 5)

NYC_Subway_Data = read_csv(file = "./Data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv")
names(NYC_Subway_Data)
NYC_Subway_Data = janitor::clean_names(NYC_Subway_Data)
names(NYC_Subway_Data)

## visual check of the data
NYC_Subway_Data
skimr::skim(NYC_Subway_Data)
```

Cleaning the data; retain line, station, name, station latitude / longitude, routes served, entry, vending, entrance type, and ADA compliance

```{r}
select(NYC_Subway_Data, line, station_name, station_latitude, station_longitude, route1, route2, route3, route4, route5, route6, route7, route8, route9, route10, route11, entrance_type, entry, vending, ada)

```

Convert the entry variable from character (YES vs NO) to a logical variable

```{r}
NYC_Subway_Data$entry <- as.logical(recode(NYC_Subway_Data$entry, "YES" = "TRUE", "NO" = "FALSE"))
view(NYC_Subway_Data$entry)


mutate(NYC_Subway_Data$entry = recode(entry, "YES" = TRUE, "NO" = FALSE))

ifelse(NYC_Subway_Data$entry, "YES", "NO")
```

The `NYC_Subway_Data` dataset contains the following variables: line, station, name, station latitude / longitude, route(s) served, entry, vending, entrance type, and ADA compliance. Thus far I selected using `select` for those previously mentioned variables and converted the entry variable from a character to a logical variable. The dimensions are 1,868 x 19. And these data are not yet tidy.

* How many distinct stations are there? Note that stations are identified both by name and by line (e.g. 125th St A/B/C/D; 125st 1; 125st 4/5); the distinct function may be useful here.

```{r}
distinct(NYC_Subway_Data, )
```

* How many stations are ADA compliant?
`sum(NYC_Subway_Data$ada, na.rm = TRUE)`


What proportion of station entrances / exits without vending allow entrance?

## Problem 2

This problem uses the Mr. Trash Wheel dataset, available as an Excel file on the course website. Please use the  HealthyHarborWaterWheelTotals2017-9-26.xlsx version.

Read and clean the Mr. Trash Wheel sheet

```{r}
library(readxl)
MrTrashWheel_Data = read_excel("./Data/HealthyHarborWaterWheelTotals2018-7-28.xlsx")
MrTrashWheel_Data = janitor::clean_names(MrTrashWheel_Data)
head(MrTrashWheel_Data, 5)


```

specify the sheet in the Excel file and to omit columns containing notes (using the range argument and cell_cols() function)
use reasonable variable names
omit rows that do not include dumpster-specific data
rounds the number of sports balls to the nearest integer and converts the result to an integer variable (using  as.integer)
Read and clean precipitation data for 2016 and 2017. For each, omit rows without precipitation data and add a variable year. Next, combine datasets and convert month to a character variable (the variable month.name is built into R and should be useful).

Write a paragraph about these data; you are encouraged to use inline R. Be sure to note the number of observations in both resulting datasets, and give examples of key variables. For available data, what was the total precipitation in 2017? What was the median number of sports balls in a dumpster in 2016?

## Problem 3

This problem uses the BRFSS data. DO NOT include this dataset in your local data directory; instead, load the data from the  p8105.datasets package.

For this question:

format the data to use appropriate variable names;
focus on the “Overall Health” topic
exclude variables for class, topic, question, sample size, and everything from lower confidence limit to GeoLocation
structure data so that values for Response (“Excellent” to “Poor”) are column names / variables which indicate the proportion of subjects with each response (which are values of Data_value in the original dataset)
create a new variable showing the proportion of responses that were “Excellent” or “Very Good”
Using this dataset, do or answer the following:

How many unique locations are included in the dataset? Is every state represented? What state is observed the most?
In 2002, what is the median of the “Excellent” response value?
Make a histogram of “Excellent” response values in the year 2002.
Make a scatterplot showing the proportion of “Excellent” response values in New York County and Queens County (both in NY State) in each year from 2002 to 2010.
